The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2024-06-24 src/paper/theory.tex
Yet another try at CI publishing
Change references to uppercase

\usepackage{microtype}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{xcolor}
\usepackage[noabbrev,nameinlink]{cleveref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}

@@

@@

The paper is organized as follows.
In \cref{sec:one_sided}, I present the main results for the case of one indispensable player and a continuum of identical fringe players.
\Cref{sec:many_sided} extends these results to the case of multiple types of fringe players.
This is where the most novel results of the paper are presented.
\Cref{sec:application} provides an example application of the results to a simple model of a two-sided market.
Finally, \cref{sec:conclusions} concludes the paper.

@@

In the following, let us assume that the assumptions required for monotonicity are always satisfied (i.e., $f$ is monotone increasing).\footnote{
    This assumption is not entirely innocuous.
    For example, having more small firms could in theory lead to stronger competition, decreasing total profits.
    However, it often holds in models with network effects \parencite{rochet2003platform} or with consumers having taste for variety \parencite{anderson2020aggregative}.
}
As a side note, it also ensures that the game is of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies.
Namely, the asymptotic and the axiomatic approach of characterizing the Shapley-value of the game both lead to the same result\footnote{
    More precisely, the asymptotic value coincides with the axiomatic one derived using the uniform distribution.
    For a more detailed discussion, see \textcite{fogelman1980asymptotic}.
}.
This result could also be used to prove \cref{prop:one_sided} instead of the direct proof provided in \cref{sec:proofs}.

@@

Because the Shapley value is a special case of the random order value, these results are quite straightforward consequences of \cref{prop:one_sided_general} and \cref{cor:fringe_value_general}.
One only has to notice that each permutation having an equal probability implies that the number of firms coming before $P$ is uniformly distributed on $1, \dots, n$, and thus the share of firms before $P$ converges in distribution to the uniform distribution on $[0, 1]$.
Alternatively, a more direct proof is provided in \cref{sec:proofs}, or a probabilistic justification can be found in \textcite{levy1997individual}.

The resulting Shapley values also have a nice geometric interpretation shown on \cref{fig:one_sided}.
Consider a rectangle with sides of length 1 and $f(1)$, respectively.
The grand coalition achieves the value $f(1)$, which is also the area of the rectangle.\footnote{
    Due to superadditivity, the grand coalition can be expected to form, and the main question is how the value is distributed between the big player and the fringe.
}
The value of the big player is then $\int_0^1 f(t) \dt$, which is simply the part of the rectangle below the graph of $f$, while the fringe gets the rest.
Thus, the graph of $f$ partitions the area (total value) into what the big player and the fringe can obtain.

@@

In words, regardless of the value of $\bar{n}$, the two types of players share the total value in the same proportion.
This proportion depends on the parameter $\alpha$ (\cref{fig:power_function_example}), which can be interpreted as the degree of substitutability between the fringe players.
More specifically, the higher $\alpha$ is, the more complementary the fringe players are to each other, and the larger the share they obtain.
In the limit, when $\alpha \to \infty$, the fringe obtains all the value, as essentially all players become indispensable, and share the total value equally.
On the other hand, when $\alpha \to 0$, the big players can appropriate all the value.

@@

For my purposes, it is sufficient to deal with the case of simple weights.
I.e., assume that there is at most one player with zero weight.
For my main result, I make use of an alternative, computational characterization of the weighted values. 
\textcite{kalai1987weighted} demonstratesd that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure.
Start with the set of all players.
Let the probability of player $i$ being the last amongst the set of remaining players $R$ be $\lambda_i / \sum_{j \in R} \lambda_j$.
Continue until all players are exhausted.
This yields a well-defined probability for each permutation of players.

@@

Now we have everything we need to derive the weighted value of both types of players.
Having \cref{eq:entry_distr_discrete} and \cref{lem:entry_distr} allows us to invoke \cref{prop:one_sided_general} to obtain the following proposition.\footnote{
    \textcite{stole1996intra} also derive essentially the same expression for the equilibrium outcome of their bargaining game with unequal profit distribution, and assert that it is equal to the weighted value.
}

@@

As before, the value of the big player can still be expressed as an integral of the value function, while the value of the fringe can be expressed as an integral of the marginal contributions of the fringe players.
The only difference is that, as in the case of the general random order value, the integrands are weighted by some probability distribution.
Depending on the shape of this distribution, regions corresponding to different masses of fringe firms can be over or underweighted in this integral, leading to different values.
Contrary to \cref{prop:one_sided_general}, the probability distribution has a specific functional form, and is characterized by a single parameter, $\lambda$.
\Cref{fig:weigh_function} illustrates the weighting function for various values of $\lambda$.

@@

First, let us examine the most general case: the random order value.
Let us start by establishing the analog of \cref{prop:one_sided_general} for the many-sided case to obtain the limit of the value of the big player.
\begin{proposition}
    \label{prop:many_sided_general}
    Let $f$ be continuous on $[0, 1]^L$. Furthermore, let us denote the random vector of the proportions of the various types of fringe players before $P$ as $X_n$:
    \begin{align*}
        X_n = \left( \frac{n_{A_1}(\mathcal{P}_P)}{n}, \dots, \frac{n_{A_L}(\mathcal{P}_P)}{n} \right).
    \end{align*}
    Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t_1, \dots, t_L)$ and (if exists) pdf $g(t_1, \dots, t_L)$.
    Then
    \begin{align*}
        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L) \\
        &= \int_0^1\dots \int_0^1 g(t_1, \dots, t_n) f(t_1, \dots, t_L) \dt_1 \dots \dt_L,
    \end{align*}
    with the last equality holding if $X$ is a continuous random variable.
\end{proposition}
The proposition above is almost identical to \cref{prop:one_sided_general}, with the only difference being that the integral is now over the $L$-dimensional unit hypercube, due to $f$ being a function of $L$ variables.

@@

Finally, player $P$'s probability of coming after $s$ proportion of the fringe is also not uniform, but rather influenced by the relationship between its own and the fringe players' weights.\footnote{
    This is the same mechanism as in the case of the one-sided weighted value.
} 
Therefore, the integral is not taken with respect to the uniform distribution, but rather one resembling that of \cref{prop:one_sided_weighted}.
The result is the following: when the big player has a higher weight, its chances of being relatively late in the ordering are higher, and thus -- due to $f$ being monotone increasing -- its value is higher.
The following, simple corollary formalizes this idea.

@@

\begin{corollary}
    \label{cor:platform_value_multiple_sides_weighted}
    $\varphi_P^\infty$ is increasing in $\lambda_P$ unless $f$ is constant.
\end{corollary}
This result is analogous to \cref{cor:platform_value_weighted}, and demonstrates that a higher weight for player $P$ corresponds to a higher value in this game as well.

@@

Following \textcite{armstrong2006competition}, let us model player entry also in a reduced form manner.
Assume that there is a continuum of potential entrants on both sides of the market.
The number of actual entrants depends on the utility they would derive from participating in the market.\footnote{
    Such assumptions are usually justified by some idiosyncratic cost of entry, the distribution of which determines the function $\phi$.
    For simplicity, I refrain from explicitly modeling this cost in the main text, but \cref{sec:explicit_entry_costs} provides a discussion of how one can incorporate it into the model, its impact on bargaining outcomes.
}
Let us denote this relationship as $\phi_i(u_i)$, where $\phi_i$ is a strictly increasing, differentiable function.
Then,
\begin{align*}
    n_i = \phi_i(u_i).
\end{align*}

@@

The characteristic function of the game takes a similar form to that in \cref{sec:many_sided}.
If the platform is not a member of a coalition, then the value that coalition can generate is zero.
Otherwise, it is simply the sum of the utilities of the two sides minus the cost of serving them.\footnote{
    Entry fees paid to the platform do not matter, as they are within-coalition transfers, and thus do not affect the total value.
}
This value, as a function of the number of entrants, is
\begin{align*}
    w(n_1, n_2) = n_1 \alpha_1 n_2^{\gamma_1} + n_2 \alpha_2 n_1^{\gamma_2} - F_1 n_1 - F_2 n_2.
\end{align*}

The share received by each type of player is then easily established using \cref{prop:many_sided_weighted}.
\begin{proposition}
    \label{prop:bargaining_entry_fees}
    The weighted values of the various sides are
    \begin{alignat*}{4}
        \pi_P^b(n_1, n_2) &= \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_P^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_P^{b_2}} \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1}}_{\coloneqq S_P^{c_1}} n_1 F_1 &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2}}_{\coloneqq S_P^{c_2}} n_2 F_2 \\
        W_1^b(n_1, n_2) &= \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_1^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_1 \gamma_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_1^{b_2}}  \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1}}_{\coloneqq S_1^{c_1}} n_1 F_1 && \\
        W_2^b(n_1, n_2) &= \underbracket{\frac{\lambda_2\gamma_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_2^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_2^{b_1}} \alpha_2 n_2 n_1^{\gamma_2} && &&- \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2}}_{\coloneqq S_2^{c_2}} n_2 F_2.
    \end{alignat*}
\end{proposition}

Total welfare $w(n_1, n_2)$ can be divided into four parts: utility generated by side $1$ and $2$, and the costs of serving side $1$ and $2$.
Each side's share of these parts is given by $S_i^{b_1}, S_i^{b_2}, S_i^{c_1}$ and $S_i^{c_2}$, respectively.
As it turns out, these shares only depend on the bargaining weights ($\lambda_P, \lambda_1, \lambda_2$) and the network effects ($\gamma_1, \gamma_2$), but not on the actual number of entrants.\footnote{
    This is due to the characteristic function being a polynomial of the number of entrants.
    Just like in \cref{sec:power_function_example}, each constituent of the polynomial are divided in a constant proportion.
}
Furthermore, all of these shares are increasing in one's own bargaining weight, and decreasing in the others' weights.
Finally, and perhaps most interestingly, the share of side $i$ from the value generated on side $j$ is also increasing in $\gamma_j$.
This means that if players on side $i$ are less substitutable (or, equivalently, more complementary) in terms of contributing to the utility of the other side, then they will receive a larger share of the value generated there.

@@

Random order values offer a comprehensive framework for modeling bargaining outcomes, and also include important and well-known special cases, such as the Shapley value or the weighted value.
Due to the former retaining many of the attractive properties of its more specialized counterparts, it might be a good candidate for modeling bargaining outcomes flexibly and in a tractable manner.
Furthermore, as shown in \cref{sec:extensions}, the results can also be generalized to cases with not completely indispensable big players, while retaining the essential structure of the results.

@@

As before, the main proposition in this section provides us with an expression of the limit of the value for this variant of the game.
Notably, as in the case of the weighted value, the share of player $P$ can again be expressed as an integral of $f$ and some weighting\footnote{
    Weighting is not a completely precise term, as $h(t)$ does not integrate to one, and is therefore not a probability distribution in this case (\cref{fig:multiple_platforms}).
} function $h(t)$, with the latter depending only on the number of big players.
\begin{proposition}
    \label{prop:multiple_platforms}
    The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
    \begin{align*}
        \varphi_{P_i}^{\infty, m} = \int_0^1 h(t) f(t) \dt,
    \end{align*}
    where $h(t) = (1-t) ^ {m-1}$.
\end{proposition}

@@

Let us examine the total value of all the big players.
Denote the aggregated value of players of type $P$ as $\varphi_{P}^{\infty, m} \coloneqq \sum_{j=1}^m\varphi_{P_j}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$.
It immediately follows from the previous proposition that
\begin{align*}
    \varphi_{P}^{\infty, m} = \int_0^1 g(t) f(t) \dt,
\end{align*}
where $g(t) = m (1-t) ^ {m-1}$.
Notice that $g(t)$ now integrates to one, and is thus a probability distribution (\cref{fig:multiple_platforms_total}).
Therefore, the Shapley value in the case of multiple, substitutable big players can be interpreted as a random order value with a single big player.
The probability distribution for the corresponding random order value has a specific form, and its only parameter is the number of big players.
Thus, all the results from the previous section apply to this case as well.

@@

Now let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
Proposition \cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
This not only means that the value of each individual big player decreases, but also that their total value goes down.

@@

It is clear that the value of the big player is decreasing in $f_0$ (\cref{fig:non_indispensable}).
Consequently, the value of the fringe is increasing in $f_0$, which is essentially its outside option (what it can achieve without the big player).
This is a natural result, and again, it is in line with what one would expect from bargaining theory.
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
                \addplot[name path=f, thick] {x^0.5};
                \addplot[name path=f0, thick] {0.3 * x^0.5};
                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
                \node[anchor=south west] at (axis cs: .8, .3*.8^0.5) {$f_0$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

Let us denote the total idiosyncratic cost incurred by all players on both sides as $K(n_1, n_2)$.
Also, suppose that if $n_i$ players enter on side $i$, then they are the ones with the lowest idiosyncratic cost.
Then, the total idiosyncratic cost is simply the sum of the idiosyncratic costs of the entrants on both sides:
\begin{align*}
    K(n_1, n_2) = \int_0^{n_1} \kappa_1(s) \ds + \int_0^{n_2} \kappa_2(s) \ds.
\end{align*}
One can obtain the weighted values of all sides using \cref{prop:many_sided_weighted}.
\begin{proposition}
    \label{prop:platform_bargaining_idiosyncratic}
    The weighted values of the idiosyncratic cost component are
    \begin{align*}
        K_P(n_1, n_2) &= \sum_{i \in \{1, 2\}} \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds, \\
        K_i(n_1, n_2) &= \lambda_i \int_0^{n_1} \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \kappa_i(s) \ds.
    \end{align*}
\end{proposition}

@@

\begin{lemma}
    \label{lemma:log_convergence}
    Let 
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n}, \\
        \Delta(s) &= \frac{1}{s}.
    \end{align*}
    Then $\Delta_n \xrightarrow[]{\mathrm{u}} \Delta$ uniformly on $[t, 1]$ for any $t > 0, \lambda > 0$.
\end{lemma}
\begin{proof}[Proof of \cref{lemma:log_convergence}]
    First, note that $\Delta_n$ and $\Delta$ are all continuous functions.
    Then, following the standard proof for $\frac{\mathrm{d}}{\mathrm{d}s}log(s) = \frac{1}{s}$ rewrite $\Delta_n(s)$ as
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n} \\
        &= \log \left( 1 + \frac{1}{sn} \right) ^ n .
    \end{align*}
    It is well known that $\left( 1 + \frac{1}{sn} \right) ^ n$ is monotone increasing in $n$ and converges to $\exp (1/s)$.
    Therefore, the pointwise convergence of $\Delta_n(s) \to \Delta(s)$ is also monotone.

>>>>

\usepackage{microtype}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{xcolor}
\usepackage[noabbrev,nameinlink]{cleveref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{snapshot}
\usepackage{apptools}
\usepackage[backend=biber,style=authoryear,maxbibnames=99,hyperref=true]{biblatex}

@@

\AtAppendix{\counterwithin{proposition}{section}}
\AtAppendix{\counterwithin{theorem}{section}}
\AtAppendix{\counterwithin{corollary}{section}}
\AtAppendix{\counterwithin{lemma}{section}}
\AtAppendix{\counterwithin{assumption}{section}}
\AtAppendix{\counterwithin{equation}{section}}
\AtAppendix{\counterwithin{figure}{section}}

@@

The paper is organized as follows.
In \Cref{sec:one_sided}, I present the main results for the case of one indispensable player and a continuum of identical fringe players.
\Cref{sec:many_sided} extends these results to the case of multiple types of fringe players.
This is where the most novel results of the paper are presented.
\Cref{sec:application} provides an example application of the results to a simple model of a two-sided market.
Finally, \Cref{sec:conclusions} concludes the paper.

@@

In the following, let us assume that the assumptions required for monotonicity are always satisfied (i.e., $f$ is monotone increasing).\footnote{
    This assumption is not entirely innocuous.
    For example, having more small firms could in theory lead to stronger competition, decreasing total profits.
    However, it often holds in models with network effects \parencite{rochet2003platform} or with consumers having taste for variety \parencite{anderson2020aggregative}.
}
As a side note, it also ensures that the game is of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies.
Namely, the asymptotic and the axiomatic approach of characterizing the Shapley-value of the game both lead to the same result\footnote{
    More precisely, the asymptotic value coincides with the axiomatic one derived using the uniform distribution.
    For a more detailed discussion, see \textcite{fogelman1980asymptotic}.
}.
This result could also be used to prove \Cref{prop:one_sided} instead of the direct proof provided in \Cref{sec:proofs}.

@@

Because the Shapley value is a special case of the random order value, these results are quite straightforward consequences of \Cref{prop:one_sided_general} and \Cref{cor:fringe_value_general}.
One only has to notice that each permutation having an equal probability implies that the number of firms coming before $P$ is uniformly distributed on $1, \dots, n$, and thus the share of firms before $P$ converges in distribution to the uniform distribution on $[0, 1]$.
Alternatively, a more direct proof is provided in \Cref{sec:proofs}, or a probabilistic justification can be found in \textcite{levy1997individual}.

The resulting Shapley values also have a nice geometric interpretation shown on \Cref{fig:one_sided}.
Consider a rectangle with sides of length 1 and $f(1)$, respectively.
The grand coalition achieves the value $f(1)$, which is also the area of the rectangle.\footnote{
    Due to superadditivity, the grand coalition can be expected to form, and the main question is how the value is distributed between the big player and the fringe.
}
The value of the big player is then $\int_0^1 f(t) \dt$, which is simply the part of the rectangle below the graph of $f$, while the fringe gets the rest.
Thus, the graph of $f$ partitions the area (total value) into what the big player and the fringe can obtain.

@@

In words, regardless of the value of $\bar{n}$, the two types of players share the total value in the same proportion.
This proportion depends on the parameter $\alpha$ (\Cref{fig:power_function_example}), which can be interpreted as the degree of substitutability between the fringe players.
More specifically, the higher $\alpha$ is, the more complementary the fringe players are to each other, and the larger the share they obtain.
In the limit, when $\alpha \to \infty$, the fringe obtains all the value, as essentially all players become indispensable, and share the total value equally.
On the other hand, when $\alpha \to 0$, the big players can appropriate all the value.

@@

For my purposes, it is sufficient to deal with the case of simple weights.
I.e., assume that there is at most one player with zero weight.
For my main result, I make use of an alternative, computational characterization of the weighted values. 
\textcite{kalai1987weighted} demonstrated that weighted values can be calculated by weighting the permutations by the probabilities arising from the following sequential ordering procedure.
Start with the set of all players.
Let the probability of player $i$ being the last amongst the set of remaining players $R$ be $\lambda_i / \sum_{j \in R} \lambda_j$.
Continue until all players are exhausted.
This yields a well-defined probability for each permutation of players.

@@

Now we have everything we need to derive the weighted value of both types of players.
Having \Cref{eq:entry_distr_discrete} and \Cref{lem:entry_distr} allows us to invoke \Cref{prop:one_sided_general} to obtain the following proposition.\footnote{
    \textcite{stole1996intra} also derive essentially the same expression for the equilibrium outcome of their bargaining game with unequal profit distribution, and assert that it is equal to the weighted value.
}

@@

As before, the value of the big player can still be expressed as an integral of the value function, while the value of the fringe can be expressed as an integral of the marginal contributions of the fringe players.
The only difference is that, as in the case of the general random order value, the integrands are weighted by some probability distribution.
Depending on the shape of this distribution, regions corresponding to different masses of fringe firms can be over or underweighted in this integral, leading to different values.
Contrary to \Cref{prop:one_sided_general}, the probability distribution has a specific functional form, and is characterized by a single parameter, $\lambda$.
\Cref{fig:weigh_function} illustrates the weighting function for various values of $\lambda$.

@@

First, let us examine the most general case: the random order value.
Let us start by establishing the analog of \Cref{prop:one_sided_general} for the many-sided case to obtain the limit of the value of the big player.
\begin{proposition}
    \label{prop:many_sided_general}
    Let $f$ be continuous on $[0, 1]^L$. Furthermore, let us denote the random vector of the proportions of the various types of fringe players before $P$ as $X_n$:
    \begin{align*}
        X_n = \left( \frac{n_{A_1}(\mathcal{P}_P)}{n}, \dots, \frac{n_{A_L}(\mathcal{P}_P)}{n} \right).
    \end{align*}
    Assume that $X_n \xrightarrow[]{d} X$ with cdf $G_X(t_1, \dots, t_L)$ and (if exists) pdf $g(t_1, \dots, t_L)$.
    Then
    \begin{align*}
        \varphi_P^\infty = \lim_{n \to \infty} \varphi_P^n &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \dG(t_1, \dots t_L) \\
        &= \int_0^1\dots \int_0^1 g(t_1, \dots, t_n) f(t_1, \dots, t_L) \dt_1 \dots \dt_L,
    \end{align*}
    with the last equality holding if $X$ is a continuous random variable.
\end{proposition}
The proposition above is almost identical to \Cref{prop:one_sided_general}, with the only difference being that the integral is now over the $L$-dimensional unit hypercube, due to $f$ being a function of $L$ variables.

@@

Finally, player $P$'s probability of coming after $s$ proportion of the fringe is also not uniform, but rather influenced by the relationship between its own and the fringe players' weights.\footnote{
    This is the same mechanism as in the case of the one-sided weighted value.
} 
Therefore, the integral is not taken with respect to the uniform distribution, but rather one resembling that of \Cref{prop:one_sided_weighted}.
The result is the following: when the big player has a higher weight, its chances of being relatively late in the ordering are higher, and thus -- due to $f$ being monotone increasing -- its value is higher.
The following, simple corollary formalizes this idea.

@@

\begin{corollary}
    \label{cor:platform_value_multiple_sides_weighted}
    $\varphi_P^\infty$ is increasing in $\lambda_P$ unless $f$ is constant.
\end{corollary}
This result is analogous to \Cref{cor:platform_value_weighted}, and demonstrates that a higher weight for player $P$ corresponds to a higher value in this game as well.

@@

Following \textcite{armstrong2006competition}, let us model player entry also in a reduced form manner.
Assume that there is a continuum of potential entrants on both sides of the market.
The number of actual entrants depends on the utility they would derive from participating in the market.\footnote{
    Such assumptions are usually justified by some idiosyncratic cost of entry, the distribution of which determines the function $\phi$.
    For simplicity, I refrain from explicitly modeling this cost in the main text, but \Cref{sec:explicit_entry_costs} provides a discussion of how one can incorporate it into the model, its impact on bargaining outcomes.
}
Let us denote this relationship as $\phi_i(u_i)$, where $\phi_i$ is a strictly increasing, differentiable function.
Then,
\begin{align*}
    n_i = \phi_i(u_i).
\end{align*}

@@

The characteristic function of the game takes a similar form to that in \Cref{sec:many_sided}.
If the platform is not a member of a coalition, then the value that coalition can generate is zero.
Otherwise, it is simply the sum of the utilities of the two sides minus the cost of serving them.\footnote{
    Entry fees paid to the platform do not matter, as they are within-coalition transfers, and thus do not affect the total value.
}
This value, as a function of the number of entrants, is
\begin{align*}
    w(n_1, n_2) = n_1 \alpha_1 n_2^{\gamma_1} + n_2 \alpha_2 n_1^{\gamma_2} - F_1 n_1 - F_2 n_2.
\end{align*}

The share received by each type of player is then easily established using \Cref{prop:many_sided_weighted}.
\begin{proposition}
    \label{prop:bargaining_entry_fees}
    The weighted values of the various sides are
    \begin{alignat*}{4}
        \pi_P^b(n_1, n_2) &= \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_P^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_P^{b_2}} \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_1}}_{\coloneqq S_P^{c_1}} n_1 F_1 &&- \underbracket{\frac{\lambda_P}{\lambda_P + \lambda_2}}_{\coloneqq S_P^{c_2}} n_2 F_2 \\
        W_1^b(n_1, n_2) &= \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_1^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_1 \gamma_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_1^{b_2}}  \alpha_2 n_2 n_1^{\gamma_2} &&- \underbracket{\frac{\lambda_1}{\lambda_P + \lambda_1}}_{\coloneqq S_1^{c_1}} n_1 F_1 && \\
        W_2^b(n_1, n_2) &= \underbracket{\frac{\lambda_2\gamma_1}{\lambda_P + \lambda_1 + \lambda_2\gamma_1}}_{\coloneqq S_2^{b_1}} \alpha_1 n_1 n_2^{\gamma_1} &&+ \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2 + \lambda_1\gamma_2}}_{\coloneqq S_2^{b_1}} \alpha_2 n_2 n_1^{\gamma_2} && &&- \underbracket{\frac{\lambda_2}{\lambda_P + \lambda_2}}_{\coloneqq S_2^{c_2}} n_2 F_2.
    \end{alignat*}
\end{proposition}

Total welfare $w(n_1, n_2)$ can be divided into four parts: utility generated by side $1$ and $2$, and the costs of serving side $1$ and $2$.
Each side's share of these parts is given by $S_i^{b_1}, S_i^{b_2}, S_i^{c_1}$ and $S_i^{c_2}$, respectively.
As it turns out, these shares only depend on the bargaining weights ($\lambda_P, \lambda_1, \lambda_2$) and the network effects ($\gamma_1, \gamma_2$), but not on the actual number of entrants.\footnote{
    This is due to the characteristic function being a polynomial of the number of entrants.
    Just like in \Cref{sec:power_function_example}, each constituent of the polynomial are divided in a constant proportion.
}
Furthermore, all of these shares are increasing in one's own bargaining weight, and decreasing in the others' weights.
Finally, and perhaps most interestingly, the share of side $i$ from the value generated on side $j$ is also increasing in $\gamma_j$.
This means that if players on side $i$ are less substitutable (or, equivalently, more complementary) in terms of contributing to the utility of the other side, then they will receive a larger share of the value generated there.

@@

Random order values offer a comprehensive framework for modeling bargaining outcomes, and also include important and well-known special cases, such as the Shapley value or the weighted value.
Due to the former retaining many of the attractive properties of its more specialized counterparts, it might be a good candidate for modeling bargaining outcomes flexibly and in a tractable manner.
Furthermore, as shown in \Cref{sec:extensions}, the results can also be generalized to cases with not completely indispensable big players, while retaining the essential structure of the results.

@@

As before, the main proposition in this section provides us with an expression of the limit of the value for this variant of the game.
Notably, as in the case of the weighted value, the share of player $P$ can again be expressed as an integral of $f$ and some weighting\footnote{
    Weighting is not a completely precise term, as $h(t)$ does not integrate to one, and is therefore not a probability distribution in this case (\Cref{fig:multiple_platforms}).
} function $h(t)$, with the latter depending only on the number of big players.
\begin{proposition}
    \label{prop:multiple_platforms}
    The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
    \begin{align*}
        \varphi_{P_i}^{\infty, m} = \int_0^1 h(t) f(t) \dt,
    \end{align*}
    where $h(t) = (1-t) ^ {m-1}$.
\end{proposition}

@@

Let us examine the total value of all the big players.
Denote the aggregated value of players of type $P$ as $\varphi_{P}^{\infty, m} \coloneqq \sum_{j=1}^m\varphi_{P_j}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$.
It immediately follows from the previous proposition that
\begin{align*}
    \varphi_{P}^{\infty, m} = \int_0^1 g(t) f(t) \dt,
\end{align*}
where $g(t) = m (1-t) ^ {m-1}$.
Notice that $g(t)$ now integrates to one, and is thus a probability distribution (\Cref{fig:multiple_platforms_total}).
Therefore, the Shapley value in the case of multiple, substitutable big players can be interpreted as a random order value with a single big player.
The probability distribution for the corresponding random order value has a specific form, and its only parameter is the number of big players.
Thus, all the results from the previous section apply to this case as well.

@@

Now let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
Proposition \Cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
This not only means that the value of each individual big player decreases, but also that their total value goes down.

@@

It is clear that the value of the big player is decreasing in $f_0$ (\Cref{fig:non_indispensable}).
Consequently, the value of the fringe is increasing in $f_0$, which is essentially its outside option (what it can achieve without the big player).
This is a natural result, and again, it is in line with what one would expect from bargaining theory.
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                    xtick={0, 1}, ytick={0}, xlabel={$s$}]
                \addplot[name path=f, thick] {x^0.5};
                \addplot[name path=f0, thick] {0.3 * x^0.5};
                \node[anchor=north west] at (axis cs: .8, .8^0.5) {$f$};
                \node[anchor=south west] at (axis cs: .8, .3*.8^0.5) {$f_0$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

Let us denote the total idiosyncratic cost incurred by all players on both sides as $K(n_1, n_2)$.
Also, suppose that if $n_i$ players enter on side $i$, then they are the ones with the lowest idiosyncratic cost.
Then, the total idiosyncratic cost is simply the sum of the idiosyncratic costs of the entrants on both sides:
\begin{align*}
    K(n_1, n_2) = \int_0^{n_1} \kappa_1(s) \ds + \int_0^{n_2} \kappa_2(s) \ds.
\end{align*}
One can obtain the weighted values of all sides using \Cref{prop:many_sided_weighted}.
\begin{proposition}
    \label{prop:platform_bargaining_idiosyncratic}
    The weighted values of the idiosyncratic cost component are
    \begin{align*}
        K_P(n_1, n_2) &= \sum_{i \in \{1, 2\}} \int_0^{n_1} \left[ 1 - \lambda_i \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \right] \kappa_i(s) \ds, \\
        K_i(n_1, n_2) &= \lambda_i \int_0^{n_1} \left( \frac{s}{n_i} \right)^{\lambda_P + \lambda_i - 1} \kappa_i(s) \ds.
    \end{align*}
\end{proposition}

@@

\begin{lemma}
    \label{lemma:log_convergence}
    Let 
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n}, \\
        \Delta(s) &= \frac{1}{s}.
    \end{align*}
    Then $\Delta_n \xrightarrow[]{\mathrm{u}} \Delta$ uniformly on $[t, 1]$ for any $t > 0, \lambda > 0$.
\end{lemma}
\begin{proof}[Proof of \Cref{lemma:log_convergence}]
    First, note that $\Delta_n$ and $\Delta$ are all continuous functions.
    Then, following the standard proof for $\frac{\mathrm{d}}{\mathrm{d}s}log(s) = \frac{1}{s}$ rewrite $\Delta_n(s)$ as
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n} \\
        &= \log \left( 1 + \frac{1}{sn} \right) ^ n .
    \end{align*}
    It is well known that $\left( 1 + \frac{1}{sn} \right) ^ n$ is monotone increasing in $n$ and converges to $\exp (1/s)$.
    Therefore, the pointwise convergence of $\Delta_n(s) \to \Delta(s)$ is also monotone.
